Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-10-09 ms.tex
phase curve fig

\shorttitle{Phase Curves of WASP-103b}
\shortauthors{Kreidberg et al.}

@@

\title{Global Climate of the Ultra-Hot Jupiter WASP-103b from \HST\ and Spitzer Phase Curve Observations}

@@

\section{Light Curve Fits}
We fit the \HST\ and \Spitzer\ phase curves independently. For each light curve fit, we used a two-component model:
 one component models the physical signal (the planet's thermal phase variation) and the other models the instrument systematics.

\subsection{Physical Model}
We explored several different models for the planet's thermal phase variation.

@@

@@

\subsection{Phase-Resolved Spectra}

>>>>

\shorttitle{Phase Curves of WASP-103\lowercase{b}}
\shortauthors{Kreidberg et al.}

@@

\title{Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}

@@

\section{Light Curve Fits}
We fit a two-component model to the full-orbit phase curves. One component models the planet signal (the thermal phase variation and transit), and the other component is a systematics model for changes in the instrument sensitivity. For each light curve, we fit the physical and systematic component simultaneously.

\subsection{Thermal Phase Variation Models}
We explored several different models for the planet's thermal phase variation. The simplest model was a sine curve, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.

We also fit climate maps using the open-source Python package \texttt{SPIDERMAN}. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and outputs a the thermal phase curve. The code is optimized to calculate

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line). The shading denotes the  1\,$\sigma$ confidence interval on the best fit. We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\section{Results}

\subsection{Phase-Resolved Spectra}
After fitting

We note that the phase-resolved spectra do not significantly change based on which model we assume for the
